\HeaderA{compute.affinities}{Probe Affinity computation}{compute.affinities}
\aliasA{base.profiles}{compute.affinities}{base.profiles}
\methaliasA{base.profiles.mm}{compute.affinities}{base.profiles.mm}
\methaliasA{base.profiles.nc}{compute.affinities}{base.profiles.nc}
\aliasA{check.probes}{compute.affinities}{check.probes}
\methaliasA{compute.affinities.local}{compute.affinities}{compute.affinities.local}
\aliasA{compute.affinity.coef}{compute.affinities}{compute.affinity.coef}
\aliasA{plotBaseProfiles}{compute.affinities}{plotBaseProfiles}
\keyword{manip}{compute.affinities}
\begin{Description}\relax
An internal function to calculate probe affinities from their
sequences.
\end{Description}
\begin{Usage}
\begin{verbatim}
compute.affinities(cdfname,verbose=TRUE)

check.probes(probepackage,cdfname)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{cdfname}] Object of class \code{character} representing the name of
\code{CDF} file associated with the arrays in the \code{AffyBatch}.
\item[\code{probepackage}] \code{character} representing the name of the
package with the probe sequence information.
\item[\code{verbose}] Logical value. If \code{TRUE} messages about the progress of
the function is printed.
\end{ldescription}
\end{Arguments}
\begin{Details}\relax
The affinity of a probe is described as the sum of position-dependent base affinities.
Each base at each position contributes to the total affinity of a probe
in an additive fashion. For a given type of base, the positional effect
is modeled as a spline function with 5 degrees of freedom.

\code{check.probes} makes sure things are matching as they should.
\end{Details}
\begin{Value}
\code{compute.affinities} returns an \code{AffyBatch} with the
affinities for PM probes in the pm locations and the affinities for MM
probes in the mm locations. NA  will be added for probes with no
sequence information.
\end{Value}
\begin{Author}\relax
Rafeal Irizarry
\end{Author}
\begin{References}\relax
Hekstra, D., Taussig, A. R., Magnasco, M., and Naef, F. (2003) Absolute mRNA concentrations from sequence-specific calibration of oligonucleotide array. Nucleic Acids Research, 31. 1962-1968.
\end{References}
\begin{SeeAlso}\relax
\code{\LinkA{gcrma}{gcrma},\LinkA{gcrma}{gcrma}}
\end{SeeAlso}

