\HeaderA{golub}{sub set of the Gene expression dataset from Golub et al. (1999)}{golub}
\methaliasA{golub.cl}{golub}{golub.cl}
\methaliasA{golub.gnames}{golub}{golub.gnames}
\keyword{datasets}{golub}
\begin{Description}\relax
Gene expression data (500 genes and 38 tumor mRNA samples) 
from the leukemia microarray study of Golub et al. 
(1999). Original data set contain 3051 genes
\end{Description}
\begin{Usage}
\begin{verbatim}
data(golub)
\end{verbatim}
\end{Usage}
\begin{Value}
\begin{ldescription}
\item[\code{golub}] matrix of gene expression levels for the 
38 tumor mRNA samples, rows correspond to genes 
(500 genes) and columns to mRNA samples.
\item[\code{golub.cl}] numeric vector indicating the tumor 
class, 27 acute lymphoblastic leukemia (ALL) cases 
(code 0) and 11 acute myeloid leukemia (AML) cases (code 1). 
\item[\code{golub.gnames}] a matrix containing the names of 
the 500 genes for the expression matrix \code{golub}. 
The three columns correspond to the gene \code{index}, 
\code{ID}, and \code{Name}, respectively.
\end{ldescription}
\end{Value}
\begin{Source}\relax
Golub et al. (1999). Molecular classification of cancer: class
discovery and class prediction by gene expression
monitoring, \emph{Science}, Vol. 286:531-537.\\
\url{http://www-genome.wi.mit.edu/MPR/}
.
\end{Source}
\begin{References}\relax
S. Dudoit, J. Fridlyand, and T. P. Speed (2002). 
Comparison of discrimination methods for the  classification 
of tumors using gene expression data. 
\emph{Journal of the American Statistical Association}, Vol. 97, No. 457, p. 77--87.
\end{References}

