\HeaderA{preprocess}{Background correct and Normalize}{preprocess}
\keyword{manip}{preprocess}
\begin{Description}\relax
This function pre-processes an \code{\LinkA{AffyBatch}{AffyBatch}}.
\end{Description}
\begin{Usage}
\begin{verbatim}
preprocess(object,subset=NULL, normalize=TRUE,background=TRUE,background.method="RMA.2",normalize.method="quantile",background.param = list(),normalize.param=list(),verbosity.level=0)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{object}] an \code{\LinkA{AffyBatch}{AffyBatch}}
\item[\code{subset}] a vector with the names of probesets to be used. If NULL
then all probesets are used.
\item[\code{normalize}] logical value. If \code{TRUE} normalize data using
quantile normalization
\item[\code{background}] logical value. If \code{TRUE} background correct
using RMA background correction
\item[\code{background.method}] name of background method to use.
\item[\code{normalize.method}] name of normalization method to use.
\item[\code{background.param}] list of parameters for background correction methods
\item[\code{normalize.param}] list of parameters for normalization methods
\item[\code{verbosity.level}] An integer specifying how much to print
out. Higher values indicate more verbose. A value of 0 will print nothing
\end{ldescription}
\end{Arguments}
\begin{Details}\relax
This function carries out background correction and normalization
pre-processing steps. It does not summarize to produce gene expression
measures. All the same pre-processing methods supplied by
\code{\LinkA{threestep}{threestep}} are supported by this function.
\end{Details}
\begin{Value}
An \code{\LinkA{AffyBatch}{AffyBatch}}
\end{Value}
\begin{Author}\relax
Ben Bolstad \email{bmb@bmbolstad.com}
\end{Author}
\begin{References}\relax
Bolstad, BM (2004) \emph{Low Level Analysis of High-density
Oligonucleotide Array Data: Background, Normalization and
Summarization}. PhD Dissertation. University of California, Berkeley.
\end{References}
\begin{SeeAlso}\relax
\code{\LinkA{expresso}{expresso}}, \code{\LinkA{rma}{rma}}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode}
data(affybatch.example)

# should be equivalent to the bg and norm of rma()
abatch.preprocessed <- preprocess(affybatch.example)

\end{ExampleCode}
\end{Examples}

