\HeaderA{threestepPLM}{Three Step expression measures returned as a PLMset}{threestepPLM}
\keyword{manip}{threestepPLM}
\begin{Description}\relax
This function converts an \code{\LinkA{AffyBatch}{AffyBatch}} into an
\code{\LinkA{PLMset}{PLMset}} using a three step expression measure.
\end{Description}
\begin{Usage}
\begin{verbatim}
threestepPLM(object,subset=NULL, normalize=TRUE,background=TRUE,background.method="RMA.2",normalize.method="quantile",summary.method="median.polish",background.param = list(),normalize.param=list(),output.param=list(), model.param=list(),verbosity.level=0)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{object}] an \code{\LinkA{AffyBatch}{AffyBatch}}
\item[\code{subset}] a vector with the names of probesets to be used. If NULL
then all probesets are used.
\item[\code{normalize}] logical value. If \code{TRUE} normalize data using
quantile normalization
\item[\code{background}] logical value. If \code{TRUE} background correct
using RMA background correction
\item[\code{background.method}] name of background method to use.
\item[\code{normalize.method}] name of normalization method to use.
\item[\code{summary.method}] name of summary method to use.
\item[\code{background.param}] list of parameters for background correction methods
\item[\code{normalize.param}] list of parameters for normalization methods
\item[\code{output.param}] list of parameters for output methods
\item[\code{model.param}] list of parameters for model methods
\item[\code{verbosity.level}] An integer specifying how much to print
out. Higher values indicate more verbose. A value of 0 will print nothing
\end{ldescription}
\end{Arguments}
\begin{Details}\relax
This function computes the expression measure using threestep
methods. It returns a \code{\LinkA{PLMset}{PLMset}}. The most important
difference is that the PLMset allows you to access the residuals
which the \code{\LinkA{threestep}{threestep}} function does not do.
\end{Details}
\begin{Value}
An \code{\LinkA{PLMset}{PLMset}}
\end{Value}
\begin{Author}\relax
Ben Bolstad \email{bmb@bmbolstad.com}
\end{Author}
\begin{References}\relax
Bolstad, BM (2004) \emph{Low Level Analysis of High-density
Oligonucleotide Array Data: Background, Normalization and
Summarization}. PhD Dissertation. University of California,
Berkeley.
\end{References}
\begin{SeeAlso}\relax
\code{\LinkA{expresso}{expresso}},
\code{\LinkA{rma}{rma}}, \code{\LinkA{threestep}{threestep}},
\code{\LinkA{rmaPLM}{rmaPLM}}, \code{\LinkA{fitPLM}{fitPLM}}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode}
data(affybatch.example)

# should be equivalent to rma()
## Not run: eset <- threestepPLM(affybatch.example)
\end{ExampleCode}
\end{Examples}

